Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-02-13 Submission.Rmd
one more minor update
bartletts

The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource. Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $K^2$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

@@

# Conclusion

>>>>

The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource. Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

@@

## Conclusion
